Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-28 vesicle_code/docs/adhesion/adhesion.tex
fixed out some figures

\begin{figure}[htp]
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm]{figs/configCartoon.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are 
  attractive.  {\em Right}: The resulting adhesive force of a single
  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
  point marked with a blue dot is repelled by the region of the vesicle
  denoted with a thick line, and attracted to the remainder of the
  vesicle.  The blue region is repelled to the right vesicle and the red
  region is attracted by the vesicle.}
\end{figure}

@@

\begin{figure}[htp]
  \begin{minipage}{0.45\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\textwidth}
    \todo[inline]{Plot of the final inclination angle of doublets that
    survive the extensional rate}
  \end{minipage}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $0.70$ submerged in an extensional flow with an extensional rate of
  $\chi$.}
\end{figure}

@@

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $0.90$, the Hamaker constant is $H=0.7$,
  the adhesion length scale is $\delta = 0.4$, and the shear rate is
  $\chi=0.5$.}
  \todo[inline]{Superimpose the background velocity on the leftmost plot
  to indicate the shearing motion}
\end{figure}
\todo[inline]{Indicate the shear flow in the right most plot.}

>>>>

\begin{figure}[htp]
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={0cm 0cm 2cm 0cm},clip]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm]{figs/configCartoon.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.31\textwidth}
    \centering
    \includegraphics[height=5cm,trim={3cm 0cm 2cm 0cm},clip]{figs/Adhesion_Force.png}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are
  attractive.  {\em Center}: Each point on a vesicle is repelled or
  attracted by all points on the other vesicles.  {\em Left}: The
  resulting adhesive force is found by integrating over all points on
  all other vesicles (equation~\eqref{eqn:adhesionForce}).  The color is
  the dot product of the adhesion force with the vector joining the
  vesicles.  Therefore, the green and blue regions are repelled by the
  other vesicle while the yellow regions are attracted to the other
  vesicle.}
\end{figure}

@@

\begin{figure}[htp]
  \begin{minipage}{0.45\textwidth}
  \centering
  \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\textwidth}
    \includegraphics[height=\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $0.70$ submerged in an extensional flow with an extensional rate of
  $\chi$.  {\em Right}: The final inclination angle of doublets.
  Results are not reported for all the low extensional rates since the
  doublet had not tilted to a steady-state inclination angle for the
  given time horizon.}
\end{figure}

@@

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $0.90$, the Hamaker constant is $H=0.7$,
  the adhesion length scale is $\delta = 0.4$, and the shear rate is
  $\chi=0.5$.}
\end{figure}
